---
title: "Exploratory Data Analysis"
author: "Mingming Pan"
date: "5/3/2022"
output:  html_document
---

```{r, include=FALSE, message=FALSE}
#Set up chunk
library(tidyverse)
library(DataExplorer)
library(lubridate)
library(forcats)
library(stringr)
library(gt)
library(ggplot2)
library(plotly)
```

```{r, include=FALSE}
#read data
netflix <- read_csv("./data/netflix_titles.csv", na = "")

#basic data exploration
plot_missing(netflix)
plot_bar(netflix)
```


```{r, include=FALSE}
#Data Cleaning
#Get day, month, year and dayofweek
#Place mutiple conetents in one cell into a list prepared for further wrangling
netflix_clean <- netflix %>%
  mutate(
    date_added   = mdy(date_added),
    year_added   = year(date_added),
    month        = month(date_added, label = TRUE, abbr = FALSE),
    day_num      = day(date_added),
    day_of_week  = wday(date_added, #day of the week
                        label = TRUE, #return name i.e "Friday"
                        abbr  = FALSE, #Return full name
                        week_start = getOption("lubridate.week.start", 1)) #1 = Monday)
    ) %>%
  mutate(country   = map(.x = country, ~str_split(.x, ", ") %>% unlist)) %>%
  mutate(listed_in = map(.x = listed_in, ~str_split(.x, ", ") %>% unlist)) %>%
  mutate(cast      = map(.x = cast, ~str_split(.x, ", ") %>% unlist)) %>%
  mutate(director  = map(.x = director, ~str_split(.x, ", ") %>% unlist)) %>%
  mutate(rating    = ifelse(str_detect(rating, "min"), NA, rating))
```

```{r, include=FALSE}
#Subset the dataset by movie and TV show
netflix_movie <- netflix_clean %>%
  filter(type == "Movie")

netflix_show <- netflix_clean %>%
  filter(type == "TV Show")
```




## Quick Glimpse of the Data Set      
```{r, echo=FALSE, message=FALSE, warning=FALSE}
plot_bar(netflix_clean, nrow = 2L, ncol = 2L)
```

- There are `r nrow(netflix_clean)` observations and `r ncol(netflix_clean)` rows in the data set.  
- There are `r nrow(netflix_movie)` movies and `r nrow(netflix_show)` TV shows in the data set.  
- TV-MA is the most frequent rating of Movies/TV shows available on Netflix.  
- Friday is the most frequent day of week that Movies/TV shows are added on Netflix.  




## Number of Movies and TV Shows Available in Top 20 Countries  
```{r, message=FALSE, echo=FALSE}
#top 20 countries
top_20 <- netflix_clean %>%
  unnest(country) %>% #unnest listed country
  filter(!is.na(country)) %>%
  pull(country) %>% 
  fct_count() %>% 
  arrange(desc(n)) %>% 
  slice(1:20) %>% 
  pull(f)

#Number of Movies and TV show in Top 20 Countries
netflix_clean %>%
  unnest(country) %>%
  filter(!is.na(country),
         country %in% top_20) %>%
  select(country, type) %>%
  group_by(country, type) %>%
  summarise(
    N = n()
  ) %>%
  ungroup() %>%
  mutate(
    country = str_to_title(country) %>%
      as.factor() %>%
      fct_reorder(N, .desc = FALSE)
    ) %>%
  ggplot(aes(x = N, y = country, fill = N)) +
  geom_bar(stat = "identity") +
  facet_wrap(~ type, scales = "free") +
  labs(
    y = "Country",
    x = "Number of Movies/TV Shows",
    title = "Number of Movies/TV Shows in Top 20 Countries"
    ) +
  scale_fill_viridis_c("Number of Movies/TV Shows", direction = -1, option = "plasma") +
  theme_classic() +
  theme(legend.position = "bottom")
```



- The number of Netflix TV shows and movies available in United States is much more than that in other countries. Other major countries have Netflix TV shows and movies available are: the United Kingdom, India, France, Canada, China.  
- Obviously, there are more movies available than TV shows.  
- It seems, there are more TV shows available than movies in Japan and South Korea.  




## Top 5 Ratings of Movies Available in Top 10 Countries      
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10}
#Top 10 countries of Movies
top_10_movie <- netflix_movie %>%
  unnest(country) %>% #unnest listed country
  filter(!is.na(country)) %>%
  pull(country) %>% 
  fct_count() %>% 
  arrange(desc(n)) %>% 
  slice(1:10) %>% 
  pull(f)

netflix_movie %>%
  select(show_id, country, rating) %>%
  unnest(country) %>%
  filter(country %in% top_10_movie) %>%
  group_by(country, rating) %>%
  summarise(
    n_movie = n()
  ) %>%
  arrange(desc(n_movie)) %>%
  group_by(country) %>%
  slice(1:5) %>%
  ungroup() %>%
  mutate(
    rating = str_to_title(rating) %>%
      as_factor() %>%
      fct_reorder2(country, n_movie, .desc = FALSE)
    ) %>%
  ggplot(aes(x = n_movie, y = rating, fill = n_movie)) +
  geom_bar(stat = "identity", width = 1, colour = "black") +
  labs(
    y = "Rating of Movies",
    x = "Number of Movies",
    title = "Top 5 Movie Ratings in the Top 10 Countries"
    )  +
  facet_wrap(~ country, scales = "free", ncol = 2) +
  theme_classic() +
  theme(legend.position = "bottom",
        axis.text.y = element_text(color = "black",
                                   size = 10,
                                   hjust = 1)) +
  scale_fill_viridis_c("# Movies", direction = -1)
```



- Except Japan and India, other top countries have R rating movies avilible in top 5 rating movies on Netflix.  
- Surprisely, R movies are the most avilaible/popular movies in United Kingdom.  





## Top 5 Ratings of TV Shows Available in Top 10 Countries    
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=10}
#Top 10 countries of TV Show
top_10_show <- netflix_show %>%
  unnest(country) %>% #unnest listed country
  filter(!is.na(country)) %>%
  pull(country) %>% 
  fct_count() %>% 
  arrange(desc(n)) %>% 
  slice(1:10) %>% 
  pull(f)

netflix_movie %>%
  select(show_id, country, rating) %>%
  unnest(country) %>%
  filter(country %in% top_10_show) %>%
  group_by(country, rating) %>%
  summarise(
    n_movie = n()
  ) %>%
  arrange(desc(n_movie)) %>%
  group_by(country) %>%
  slice(1:5) %>%
  ungroup() %>%
  mutate(
    country = str_to_title(country) %>%
      as_factor() %>%
      fct_reorder(n_movie, .desc = TRUE)
    ) %>%
  ggplot(aes(x = n_movie, y = rating, fill = n_movie)) +
  geom_bar(stat = "identity", width = 1, colour = "black") +
  labs(
    y = "Rating of TV Shows",
    x = "Number of TV Shows",
    title = "Top 5 TV Shows Ratings in the Top 10 Countries"
    ) +
  scale_fill_viridis_c("# TV Shows", direction = -1) +
  facet_wrap(~ country, scales = "free", ncol = 2) +
  theme_classic() +
  theme(legend.position = "bottom",
        axis.text.y = element_text(color = "black",
                                   size = 10,
                                   hjust = 1))
```

- The top 10 countries have some differnces from movies and TV shows. From movies to TV shows, Mexico, China and Germany are switched to Australia, South Korea and Taiwan.   
- R TV shows are not very avilible/popular in Japan, South Korea, India, and Taiwan.    
- Not surprisely, R TV shows again are the most avilaible TV shows in United Kingdom.   




## Trend of Movies and TV Shows Added in Top 10 Countries in Recent Years
```{r, warning=FALSE, echo=FALSE, message=FALSE ,fig.width=15}
#Top 10 countries
top_10 <- netflix_clean %>%
  unnest(country) %>% #unnest listed country
  filter(!is.na(country)) %>%
  pull(country) %>% 
  fct_count() %>% 
  arrange(desc(n)) %>% 
  slice(1:10) %>% 
  pull(f)

#Trend change in Top 10 countries
netflix_clean %>%
  select(country, year_added, type) %>%
  unnest(country) %>% 
  filter(
    !is.na(country), 
    !is.na(year_added),
    country %in% top_10
    ) %>%
  group_by(country, year_added, type) %>%
  summarise(
    N = n()
  ) %>%
  ungroup() %>%
  ggplot(aes(x = year_added, y = N, colour = type, fill = type)) +
  stat_smooth(alpha   = 0.2, 
              size    = 1.2,
              span    = 0.5,
              formula = "y ~ x",
              se      = FALSE) +
  geom_point(alpha    = 0.85,
             position = "jitter",
             size     = 1.5, 
             shape    = 16) +
  facet_wrap(~ country, scale = "free_y", ncol = 5) +
  labs(
    x = "Year Added",
    y = "Number of Movies/ TV Shows",
    title = "Trend of Movies and TV Shows Added in Top 10 Countries in Recent Years"
  ) +
  theme_classic() +
  theme(legend.position = "bottom")
```



 
- Most top countries have obviouly more movies added than TV shows added in recent years, while this is not true for Japan and South Korea.  










