---
title: "EDA"
author: "Mingming Pan"
date: "5/3/2022"
output:  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
---

```{r, include=FALSE, message=FALSE}
library(tidyverse)
library(DataExplorer)
library(lubridate)
library(forcats)
library(stringr)
library(gt)
library(ggplot2)
```


#Understanding what content is available in different countries. Are there any differences between movies and TV shows?
#Does Netflix have more focus on TV Shows than movies in recent years in different countries and regions? Are there any duration changing trends?
```{r, include=FALSE}
#read data
netflix <- read_csv("./data/netflix_titles.csv", na = "")

#basic data exploration
plot_missing(netflix)
plot_bar(netflix)
```

```{r}
#glimpse the dataset
head(netflix, n = 20)
```

```{r}
#Data Cleaning
#Get day, month, year and dayofweek
#Place mutiple conetents in one cell into a list prepared for further wrangling
netflix_clean <- netflix %>%
  mutate(
    date_added   = mdy(date_added),
    year_added   = year(date_added),
    month        = month(date_added, label = TRUE, abbr = FALSE),
    day_num      = day(date_added),
    day_of_week  = wday(date_added, #day of the week
                        label = TRUE, #return name i.e "Friday"
                        abbr  = FALSE, #Return full name
                        week_start = getOption("lubridate.week.start", 1)) #1 = Monday)
    ) %>%
  mutate(country   = map(.x = country, ~str_split(.x, ", ") %>% unlist)) %>%
  mutate(listed_in = map(.x = listed_in, ~str_split(.x, ", ") %>% unlist)) %>%
  mutate(cast      = map(.x = cast, ~str_split(.x, ", ") %>% unlist)) %>%
  mutate(director  = map(.x = director, ~str_split(.x, ", ") %>% unlist)) %>%
  mutate(rating    = ifelse(str_detect(rating, "min"), NA, rating))
```


```{r}
plot_bar(netflix_clean)
```
#n_movie and n_show
#Why arrange is not working?
```{r}
#top 20 countries
top_20 <- netflix_clean %>%
  unnest(country) %>% #unnest listed country
  filter(!is.na(country)) %>%
  pull(country) %>% 
  fct_count() %>% 
  arrange(desc(n)) %>% 
  slice(1:20) %>% 
  pull(f)

#Number of Movies and TV show in Top 20 Countries
netflix_clean %>%
  unnest(country) %>%
  filter(!is.na(country),
         country %in% top_20) %>%
  select(country, type) %>%
  group_by(type, country) %>%
  summarise(
    N = n()
  ) %>%
  arrange(country, desc(N)) %>%
  gt() %>%
  tab_header("Number of Movies and TV show in Top 20 Countries")
```

 group_by(branch, location) %>%
  summarise(
    N = n()
  ) %>%
  arrange(branch, desc(N)) %>%
  group_by(branch) %>%
  slice(1:5)


```{r}
#Subset the dataset by movie and TV show
netflix_movie <- netflix_clean %>%
  filter(type == "Movie")

netflix_show <- netflix_clean %>%
  filter(type == "TV Show")
```

#Understanding what content is available in different countries. Are there any differences between movies and TV shows?
#Does Netflix have more focus on TV Shows than movies in recent years in different countries and regions? Are there any duration changing trends?

#Top 5 ratings in top 10 countries
#Movies
```{r}
#Top 10 countries
top_10 <- netflix_movie %>%
  unnest(country) %>% #unnest listed country
  filter(!is.na(country)) %>%
  pull(country) %>% 
  fct_count() %>% 
  arrange(desc(n)) %>% 
  slice(1:10) %>% 
  pull(f)

netflix_movie %>%
  select(show_id, country, rating) %>%
  unnest(country) %>%
  filter(country %in% top_10) %>%
  group_by(country, rating) %>%
  summarise(
    n_movie = n()
  ) %>%
  arrange(desc(n_movie)) %>%
  group_by(country) %>%
  slice(1:5) %>%
  ungroup() %>%
  mutate(
    country = str_to_title(country) %>%
      as_factor() %>%
      fct_reorder(n_movie, .desc = TRUE),
    rating = str_to_title(rating) %>%
      as_factor() %>%
      fct_reorder2(country, n_movie, .desc = FALSE)
    ) %>%
  ggplot(aes(x = n_movie, y = rating, fill = n_movie)) +
  geom_bar(stat = "identity", width = 1, colour = "black") +
  labs(
    y = "Rating of Movies",
    x = "Number of Movies",
    title = "Top 5 Movie Ratings in the Top 10 Countries"
    ) +
  theme(legend.position = "right",
        axis.text.y = element_text(color = "black",
                                   size = 10,
                                   hjust = 1)) +
  scale_fill_viridis_c("# Movies", direction = -1) +
  facet_wrap(~ country, scales = "free_y", ncol = 2)
```
#listed in and country both are stored in list how to unnest both?
```{r}
#Top 10 countries
top_10 <- netflix_show %>%
  unnest(country) %>% #unnest listed country
  filter(!is.na(country)) %>%
  pull(country) %>% 
  fct_count() %>% 
  arrange(desc(n)) %>% 
  slice(1:10) %>% 
  pull(f)

netflix_movie %>%
  select(show_id, country, rating) %>%
  unnest(country) %>%
  filter(country %in% top_10) %>%
  group_by(country, rating) %>%
  summarise(
    n_movie = n()
  ) %>%
  arrange(desc(n_movie)) %>%
  group_by(country) %>%
  slice(1:5) %>%
  ungroup() %>%
  mutate(
    country = str_to_title(country) %>%
      as_factor() %>%
      fct_reorder(n_movie, .desc = TRUE),
    rating = str_to_title(rating) %>%
      as_factor() %>%
      fct_reorder2(country, n_movie, .desc = FALSE)
    ) %>%
  ggplot(aes(x = n_movie, y = rating, fill = n_movie)) +
  geom_bar(stat = "identity", width = 1, colour = "black") +
  labs(
    y = "Rating of TV Shows",
    x = "Number of TV Shows",
    title = "Top 5 TV Shows Ratings in the Top 10 Countries"
    ) +
  theme(legend.position = "right",
        axis.text.y = element_text(color = "black",
                                   size = 10,
                                   hjust = 1)) +
  scale_fill_viridis_c("# TV Shows", direction = -1) +
  facet_wrap(~ country, scales = "free_y", ncol = 2)
```
#Taiwan, South Korean and Australia <-> Mexico, China, Germany


#More focus on movies or TV shows in different countries?
#Why 
```{r}
#Top 6 countries
top_6 <- netflix_clean %>%
  unnest(country) %>% #unnest listed country
  filter(!is.na(country)) %>%
  pull(country) %>% 
  fct_count() %>% 
  arrange(desc(n)) %>% 
  slice(1:6) %>% 
  pull(f)

#Trend change in Top 6 countries
netflix_clean %>%
  select(country, year_added, type) %>%
  unnest(country) %>% 
  filter(
    !is.na(country), 
    !is.na(year_added),
    country %in% top_6
    ) %>%
  group_by(country, year_added, type) %>%
  summarise(
    N = n()
  ) %>%
  ungroup() %>%
  ggplot(aes(x = year_added, y = N, colour = type, fill = type)) +
  stat_smooth(alpha   = 0.2, 
              size    = 1.2,
              formula = "y ~ x",
              se      = FALSE) +
  geom_point(alpha    = 0.85,
             position = "jitter",
             size     = 1.5, 
             shape    = 16) +
  facet_wrap(~ country) +
  labs(
    x = "Year",
    y = "Number of Movies/ TV Shows",
    title = "Trend of Movies and TV Shows Added in Top 6 Countries"
  )
```
#Conclusion: From the plots, we can conclude that. 

```{r}

```

```{r}

```









